Buildtime Trend : What's trending in your build process

### 2015-04-05 buildtimetrend/presentation.tex
mention first adopters
add more advice
some improvements
add link to presentation location

      \item get advice from a friend or colleague

@@

          \item online tools : Landscape.io, Scrutinizer

@@

@@

>>>>

      \item read code from other projects
      \item get advice from friends and colleagues

@@

          \item online tools : Landscape.io, Scrutinizer, Codacy

@@

      \item the Open Source projects testdriving the service

@@

    Presentation available on \href{https://ruleant.github.io/presentations/}{\small{https://ruleant.github.io/presentations/}}
